Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-26 paper/ms.tex
Halo material removed sentence
Remove hi res sentence

Second, we measure the angle offset between the halo wake and the bar. If the
wake and the bar are aligned (i.e., there is no angle offset), then the wake
cannot exert a negative torque on the bar. This angle is plotted in the left
panel of Fig.~\ref{fig:wake}, which shows that the angle offset is larger in the
\Nbody{} case than in the \SMUGGLE{} case by about a factor of {\bf three}. The
center and right panels of Fig.~\ref{fig:wake} show the halo wake with respect
to the location of the bar in the \Nbody{} (center) and \SMUGGLE{} (right) cases
at one point in time.

@@

\begin{figure*}
    \centering
    \includegraphics[width=9cm]{fig/ps_star.pdf}
    \caption{{\bf Pattern speed evolution of a model in which we instaneously
    add stars instead of gas to the simulation, with the same density profile as
    the gas phase. The pattern speed evolution in this case is qualitatively
    similar to that of the $N$-body case, with a slight offset in the pattern
    speed. This test demonstrates that the stable pattern speed evolution in the
    SMUGGLE case is not simply a consequence of the change in potential imposed
    in our initial conditions.} \textcolor{red}{This will be updated with a
    higher resolution run.}}
\label{fig:ps-star}
\end{figure*}

>>>>

Second, we measure the angle offset between the halo wake and the bar. If the
wake and the bar are aligned (i.e., there is no angle offset), then the wake
cannot exert a negative torque on the bar. This angle is plotted in the left
panel of Fig.~\ref{fig:wake}, which shows that the angle offset is larger in the
\Nbody{} case than in the \SMUGGLE{} case by about a factor of {\bf three}. The
center and right panels of Fig.~\ref{fig:wake} show the halo wake with respect
to the location of the bar in the \Nbody{} (center) and \SMUGGLE{} (right) cases
at one point in time. {\bf Note that in Fig.~\ref{fig:wake} we have removed the
halo material trapped in the bar, which exerts no net torque on the bar.}

@@

\begin{figure*}
    \centering
    \includegraphics[width=9cm]{fig/ps_star.pdf}
    \caption{{\bf Pattern speed evolution of a model in which we instaneously
    add stars instead of gas to the simulation, with the same density profile as
    the gas phase. The pattern speed evolution in this case is qualitatively
    similar to that of the $N$-body case, with a slight offset in the pattern
    speed. This test demonstrates that the stable pattern speed evolution in the
    SMUGGLE case is not simply a consequence of the change in potential imposed
    in our initial conditions.}}
\label{fig:ps-star}
\end{figure*}
